### 2021-09-09 presentation/presentation.tex
update presentation

\documentclass[aspectratio=169]{beamer}

\mode<presentation>
{
  \usetheme{Luebeck}
  % \usetheme{Madrid}
  % \usetheme{Warsaw}
  % \usetheme{Copenhagen}
  % \usecolortheme{beaver}
  % \usecolortheme{rose}
  % or ...
  % \usecolortheme{beaver}
  \useoutertheme{split}
  \useinnertheme{circles}
\definecolor{supelecRed}{RGB}{120,30,56}
\definecolor{supelecPurple}{RGB}{104,95,115}
%
  % \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette primary}{bg=supelecRed}
  % \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette secondary}{bg=supelecRed}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  % \setbeamercolor{palette tertiary}{bg=supelecPurple}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!90}
  % \setbeamercolor{palette quaternary}{bg=supelecPurple}
  % \setbeamercolor{block title}{bg=red!50!black!70}
  \setbeamercolor{block title}{bg=supelecRed}

@@

\usepackage[english]{babel}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning}
\usetikzlibrary{overlay-beamer-styles}
\usepackage{pgfplots}
 \usetikzlibrary{plotmarks}
  \usetikzlibrary{arrows.meta}
  \usepgfplotslibrary{patchplots}
  \usepackage{grffile}
% or whatever

@@

@@

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

@@

\begin{frame}{Context}
  \begin{figure}
    \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
    \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
    \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
    \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
  \end{figure}
  \only<5->{
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<6> Geographically distributed
      \item<7> Coupled by constraints (energy)
      \item<8> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<9> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
\end{frame}

@@

  \begin{figure}
    \centering
    \foreach \i in {1,...,10}{%
      % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
      \only<{\i}>{\input{../img/mpcState\i.tex}}%
      \only<{\i}>{\input{../img/mpcControl\i.tex}}%
    }
  \end{figure}
\end{frame}

\begin{frame}[label=current]
  \begin{itemize}
    \item Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item Solution: Divide and Conquer
  \end{itemize}
  \vfill
  \begin{figure}
    \centering
    \only<1>{
    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
      \node[draw,
      rectangle,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{3}>{fill=supelecRed!90,text=white},
      minimum width=3.5cm,
      minimum height=4cm
      ] (block1) {MPC};
    \end{tikzpicture}
    }%
    \only<2>{
      \tikzset{mpcSmall/.style={
      rectangle,
      align=center,
      fill=supelecRed!10,
      minimum width=2.cm,
      minimum height=.5cm},
    coordinator/.style={
    rectangle,
    trapezium stretches,
    align=center,
    fill=supelecRed!10,
    minimum width=1cm,
    minimum height=4cm
    }}
  \begin{tikzpicture}[font=\small,thick,node distance=.35cm and .5cm]

    \node[draw,
    mpcSmall
    ] (block1) {MPC};

    \node[draw,
    mpcSmall,
    below=of block1,
    ] (block2) {MPC};

    \node[draw,
    mpcSmall,
    below=of block2,
    ] (block3) {MPC};

    \node[draw,
    mpcSmall,
    fill=none,
    draw=white,
    below=of block3,
    ] (block4) {\vdots};
    \node[draw,
    mpcSmall,
    below=of block4,
    ] (block5) {MPC};

@@

\draw (block2) -- (coordinator);
\draw (block3) -- (coordinator);

  \end{tikzpicture}
}%

\end{figure}
\end{frame}

% \begin{frame}
%   \centering
%   \begin{minipage}{.65\linewidth}
%     \begin{algorithm}[H]
%       \DontPrintSemicolon
%       Coordinator initializes $\vec{\theta}^{(0)}$ \;
%       $p:=0$\;
%       \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
%         Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
%         Coordinator updates allocations~\eqref{eq:thetaNegot}\;
%         $p:=p+1$
%       }
%       \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
%     \end{algorithm}
%   \end{minipage}
% \end{frame}

\begin{frame}
  \begin{figure}
    \centering
    \scalebox{.6}{
      \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
        \node[draw,
        rounded rectangle,
        fill=gray!90!black!50,
        alt=<{2}>{fill=supelecRed!90,text=white},
        minimum width=2.5cm,
        minimum height=1cm] (block1) {Start};

@@

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

@@

\subsection{The Basic Problem That We Studied}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

\begin{frame}{Make Titles Informative.}
  \begin{block}{te}

  \end{block}
  You can create overlays\dots
  \begin{itemize}
  \item using the \texttt{pause} command:
    \begin{itemize}
    \item
      First item.
      \pause
    \item
      Second item.
    \end{itemize}
  \item
    using overlay specifications:
    \begin{itemize}
    \item<3->
      First item.
    \item<4->
      Second item.
    \end{itemize}
  \item
    using the general \texttt{uncover} command:
    \begin{itemize}
      \uncover<5->{\item
        First item.}
      \uncover<6->{\item
        Second item.}
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Previous Work}

@@

\section{Securing the DMPC}
% \begin{frame}
% \SetKwBlock{negotPhase}{ Negotiation Phase:}{}
% \SetKwBlock{detectPhase}{ Detection Phase:}{}
% \scalebox{.8}{  \begin{algorithm}[H]
%     \DontPrintSemicolon
%     \detectPhase{
%     $h:=0$\;
%     \Repeat{
%     $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
%   }{
%     Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
%     Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
%     Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
%     $h:=h+1$\;
%   }
%     Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
%   }
%     \negotPhase{
%     Coordinator initializes $\vec{\theta}^{(0)}$ \;
%     $p:=0$\;

@@

\begin{frame}
  \begin{figure}[h]
    \centering
  \scalebox{.6}{
    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
      \draw[loosely dashed,
      minimum width=2.5cm,
      minimum height=1cm] (8cm,1cm) -- (8cm,-10cm);

@@

\section{Our Results/Contribution}

\subsection{Main Results}

\subsection{Basic Ideas for Proofs/Implementation}

\section*{Summary}

\begin{frame}{Summary}
  \pause
  \begin{minipage}[t]{.45\textwidth}
    % Keep the summary *very short*.
    \begin{enumerate}
      \item
            Resource allocation based DMPC is vulnerable to attacks.
            \pause
      \item
            Sub-problems structure has time invariant parameters.
            \pause
      \item
            Attacks can be detected using these parameters.
    \end{enumerate}
  \end{minipage}
  \pause
    % The following outlook is optional.
    % \vskip0pt plus.5fill
  \begin{minipage}[t]{.45\textwidth}
    \begin{itemize}
      \item Outlook
            \pause
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
                    \pause
              \item
                    Non-linear attack model
            \end{itemize}
    \end{itemize}
  \end{minipage}
\end{frame}

@@

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}
\begin{frame}[plain]
  \centering
  \vfill
  Questions?
  \vfill
  \begin{minipage}[t]{.45\linewidth}
    \small
    \centering
    Repository
    \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}

>>>>

\documentclass[aspectratio=169]{beamer}
% \includeonlyframes{current}

\mode<presentation>
{
  \usetheme{Luebeck}
  % \usetheme{Madrid}
  % \usetheme{Warsaw}
  % \usetheme{Copenhagen}
  % \usecolortheme{beaver}
  % \usecolortheme{rose}
  % or ...
  % \usecolortheme{beaver}
  \useoutertheme{split}
  \useinnertheme{circles}
  \usefonttheme[onlymath]{serif}
\definecolor{supelecRed}{RGB}{120,30,56}
\definecolor{supelecPurple}{RGB}{104,95,115}
%
  % \setbeamercolor{palette primary}{bg=red!50!black!80}
  \setbeamercolor{palette primary}{bg=supelecRed}
  % \setbeamercolor{palette secondary}{bg=red!50!black!70}
  \setbeamercolor{palette secondary}{bg=supelecRed}
  \setbeamercolor{palette tertiary}{bg=gray!90!black!50}
  % \setbeamercolor{palette tertiary}{bg=supelecPurple}
  \setbeamercolor{palette quaternary}{bg=gray!90!black!90}
  % \setbeamercolor{palette quaternary}{bg=supelecPurple}
  % \setbeamercolor{block title}{bg=red!50!black!70}
  \setbeamercolor{block title}{bg=supelecRed}
  \setbeamercolor{block title example}{bg=gray!90!black!90}
  \setbeamercolor{block title example}{bg=gray!90!black!90}

@@

\usepackage[english]{babel}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning}
\usetikzlibrary{overlay-beamer-styles}
\usepackage{pgfplots}
\usepackage{amssymb}
 \usetikzlibrary{plotmarks}
  \usetikzlibrary{arrows.meta}
  \usepgfplotslibrary{patchplots}
  \usepackage{grffile}
\usepackage{booktabs}       % filenames
% or whatever

@@

\newtheorem{assumption}{Assumption}%[numberby]

@@

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,subsectionstyle=show/show/shaded]
  \end{frame}
}

@@

% \begin{frame}{Context}
%   \begin{figure}
%     \includegraphics<1>[width=.6\textwidth]{the_city_nothing.pdf}%
%     \includegraphics<2>[width=.6\textwidth]{the_city_houses.pdf}%
%     \includegraphics<3>[width=.6\textwidth]{the_city_buildings.pdf}%
%     \includegraphics<4>[width=.6\textwidth]{the_city_cars.pdf}%
%   \end{figure}
%   \only<5->{
%   \begin{minipage}{.45\textwidth}
%     \includegraphics[width=\textwidth]{the_city_cars.pdf}%
%   \end{minipage}
%   \begin{minipage}{.5\textwidth}
%     \begin{itemize}
%       \item<6> Geographically distributed
%       \item<7> Coupled by constraints (energy)
%       \item<8> Optimization objectives
%             \begin{itemize}
%               \item Energy
%               \item User satisfaction
%               \item \dots
%             \end{itemize}
%       \item<9> Solution $\to$ Model Predictive Control
%     \end{itemize}
%   \end{minipage}
%   }
% \end{frame}

\begin{frame}{Context}
  \centering
  Smart City\\
  \begin{minipage}{.45\textwidth}
    \includegraphics[width=\textwidth]{the_city_cars.pdf}%
  \end{minipage}
  \only<2-5>{
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<2> Energy Distribution System
      \item<3> Traffic management
      \item<4> Heat distribution
      \item<5> Water distribution
      \item<5>[] \dots
    \end{itemize}
  \end{minipage}
  }
\only<6->{
  \begin{minipage}{.5\textwidth}
    \begin{itemize}
      \item<6> Geographically distributed
      \item<7> Coupled by constraints (energy)
      \item<8> Optimization objectives
            \begin{itemize}
              \item Energy
              \item User satisfaction
              \item \dots
            \end{itemize}
      \item<9> Solution $\to$ Model Predictive Control
    \end{itemize}
  \end{minipage}
  }
\end{frame}

@@

  \begin{figure}
    \centering
    \foreach \i in {1,...,4}{%
      % \includegraphics<\i>[width=.5\textwidth]{mpc\i.pdf}%
      \only<{\i}>{\input{../img/mpcState\i.tex}}%
      \only<{\i}>{\input{../img/mpcControl\i.tex}}%
    }
  \end{figure}
\end{frame}

\begin{frame}{Distributed Model Predictive Control}
  \begin{itemize}
    \item<1> Problem: Complexity depends on $N_{p},m,p$ and sizes of $\vec{x}$ and $\vec{u}$
    \item<2> Solution: Divide and Conquer
  \end{itemize}
  \vfill
  \centering
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}
      \centering
      \only<1>{
        \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
          \node[draw,
          rectangle,
          trapezium stretches,
          align=center,
          fill=supelecRed!10,
          alt=<{3}>{fill=supelecRed!90,text=white},
          minimum width=3.5cm,
          minimum height=4cm
          ] (block1) {MPC};
        \end{tikzpicture}
      }%
      \only<2>{
        \begin{tikzpicture}[font=\small,thick,node distance=.2cm and .5cm,
          mpcSmall/.style={
            rectangle,
            align=center,
            fill=supelecRed!10,
            minimum width=2.cm,
            minimum height=.4cm},
          coordinator/.style={
            rectangle,
            align=center,
            fill=supelecRed!10,
            minimum width=1cm,
            minimum height=4cm
          } ]

          \node[draw,
          mpcSmall
          ] (block1) {MPC M};

          \node[draw,
          mpcSmall,
          fill=none,
          draw=white,
          below=of block1,
          ] (block2) {\vdots};

          \node[draw,
          mpcSmall,
          below=of block2,
          ] (block3) {MPC 3};

          \node[draw,
          mpcSmall,
          below=of block3,
          ] (block4) {MPC 2};
          \node[draw,
          mpcSmall,
          below=of block4,
          ] (block5) {MPC 1};

@@

          \draw[latex-latex] (block1.east) -- (block1.east -| coordinator.west);
          \draw[latex-latex] (block3.east) -- (block3.east -| coordinator.west);
          \draw[latex-latex] (block4.east) -- (block4.east -| coordinator.west);
          \draw[latex-latex] (block5.east) -- (block5.east -| coordinator.west);

        \end{tikzpicture}
      }%
    \end{figure}
  \end{minipage}
\end{frame}

\begin{frame}{Distributed Model Predictive Control}{Quantity Decomposition | Resource Allocation}
  \centering
  \only<4>{
    \begin{minipage}[t]{.3\linewidth}
      \begin{figure}[!t]
        \scalebox{.7}{\footnotesize \def\svgwidth{8cm} \input{../img/diagQuantMod.pdf_tex}}
      \end{figure}
    \end{minipage}
    \hfill
  }
  \only<1>{
    \begin{equation*}
      \scalebox{1}{
        $\displaystyle
        \begin{matrix}
          \underset{\vec{u}_i(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\overbrace{\sum\limits^{M}_{i=1} \overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}}^{\textstyle J_{G}(k)}\\
          \mathrm{subject~ to}&
          \left.
            \begin{matrix}
              \vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
              \sum^{M}_{i=1}\Gamma_{i}\vec{u}_{i}(k)=\vec{u}_{\mathrm{\max}}\\
            \end{matrix}
          \right\}
          \begin{aligned}
            &\forall i\in\{1,\dots,M\}\\
            &\forall j\in\{1,\dots,N_{p}\}
          \end{aligned}
        \end{matrix}
        $}
    \end{equation*}
  }
  \only<2->{
    \begin{minipage}[t]{.6\linewidth}
      \centering
      \begin{equation*}
        \scalebox{.8}{
          $\displaystyle
          \left.
            \small
            \begin{aligned}
              J_{i}^{\star}(\vec{\theta}_{i}(k))&=\underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}J_i(k)\\
              \mathrm{s.t.} &\quad\vec{x}_{i}(k+1)=A_{i}\vec{x}_{i}(k) + B_{i}\vec{u}_{i}(k)\\
              &\quad\Gamma_{i}\vec{u}_i(k)=\vec{\theta}_{i}(k):\vec{\lambda}_{i}(k)\\
            \end{aligned}
          \right\}
          \small
          \begin{aligned}
            &\forall i\in\{1,\dots,M\}\\
            &\forall j\in\{1,\dots,N_{p}\}
          \end{aligned}
          \label{eq:DOP_local}
          $}
      \end{equation*}
      \vfill
      \begin{equation*}
        \small
        \begin{aligned}
          \only<2>{
            J^{\star}&=\underset{\vec{\theta}(k:k+N_{p}-1|k)}{\mathrm{minimize}}\sum^{M}_{i=1} J^{\star}_i(\vec{\theta}_i(k))\\
            \mathrm{s.t.} &\quad \sum_{i=1}^{M}\vec{\theta}_{i}(k)=\vec{u}_{\max}
          }
          \only<3->{
            \vec{\theta}_{i}\pplusone=\vec{\theta}_{i}\p+\rho\left(\vec{\lambda}_{i}^{\star}(\vec{\theta}_{i}\p)-\frac{1}{M}\sum^{M}_{j=1} \vec{\lambda}_{j}^{\star}(\vec{\theta}_{j}\p)\right)
          }
        \end{aligned}
      \end{equation*}
    \end{minipage}
  }
\end{frame}
% \begin{frame}
%   \centering
%   \begin{minipage}{.65\linewidth}
%     \begin{algorithm}[H]
%       \DontPrintSemicolon
%       Coordinator initializes $\vec{\theta}^{(0)}$ \;
%       $p:=0$\;
%       \Repeat{$\|\vec{\theta}^{(p)} -\vec{\theta}^{(p-1)}\|\leq\epsilon$}{
%         Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}\p)$\;
%         Coordinator updates allocations~\eqref{eq:thetaNegot}\;
%         $p:=p+1$
%       }
%       \caption{Quantity decomposition based DMPC.}\label{alg:quantityAlg}
%     \end{algorithm}
%   \end{minipage}
% \end{frame}

\begin{frame}{Quantity Decomposition | Resource Allocation}
  \begin{figure}
    \centering
    \scalebox{.55}{
      \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
        \node[draw,
        rounded rectangle,
        fill=gray!90!black!50,
        alt=<{2}>{fill=supelecRed!90,text=white},
        minimum width=2.5cm,
        minimum height=1cm] (block1) {Start};

@@

\begin{frame}{}
  \centering
  \vfill
What if agents send a non-agreed $\vec{\lambda}_{i}$?
  \vfill
\end{frame}

\begin{frame}{Outline}
  % \tableofcontents
  \tableofcontents[subsectionstyle=show/show/show]
  % You might wish to add the option [pausesections]
\end{frame}

@@

\subsection{Attacks}

\begin{frame}{How can a non-cooperative agent attack?}

  \begin{itemize}
    \item<1-> $\vec{\lambda}_{i}$ is the only interface with coordination
    \item<2-> Non-cooperative agent sends $\tilde{\vec{\lambda}}_{i}=\gamma_{i}(\vec{\lambda}_{i})$\pause
  \end{itemize}

\end{frame}

\subsection{Consequences}
\begin{frame}{Example}
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}[!t]
      \centering
      \begin{tikzpicture}
        \node (0,0){\includegraphics[width=\textwidth]{changeOfJ.pdf}};
        \draw<4>[rounded corners,red,thick] (-2.5,2.5) rectangle +(.5,-5);
        \draw<5>[rounded corners,red,thick] (2.5,2.5) rectangle +(.75,-5);
      \end{tikzpicture}
    \end{figure}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{.45\linewidth}
    \begin{exampleblock}{4 distinct agents}
      \begin{itemize}
        \item<2-> Agent 1 is non-cooperative\\
        \item<3-> It uses $\tilde{\vec{\lambda}}_{1}=\gamma_{1}(\vec{\lambda}_{1})=\tau_{1}I\vec{\lambda}_{1}$
      \end{itemize}
    \end{exampleblock}
  \end{minipage}
\end{frame}

@@

\section{Securing the DMPC}

\subsection{Analysis of Subproblems}

\begin{frame}
  \frametitle{Quadratic Case}
  \only<1>{
    \begin{equation*}
      % \scalebox{.8}{
      %   $\displaystyle
          \small
          \begin{aligned}
            \underset{\vec{u}_{i}(k:k+N_{p}-1|k)}{\mathrm{minimize}}&\overbrace{\sum_{j=1}^{N_{p}}\|\vec{v}_i(k+j|k)\|^{2}_{Q_i}+\|\vec{u}_i(k+j-1|k)\|^{2}_{R_i}}^{\textstyle J_{i}(k)}\\
            \mathrm{s.t.} &
            \left.
              \begin{aligned}
                \vec{x}_{i}(\xi+1)=A_{i}\vec{x}_{i}(\xi) + B_{i}\vec{u}_{i}(\xi)\\
                \Gamma_{i}\vec{u}_i(\xi)=\vec{\theta}_{i}(\xi):\vec{\lambda}_{i}(\xi)\\
              \end{aligned}
            \right\}
            \small
            \begin{aligned}
              &\forall \xi\in\{1,\dots,N_{p}\}
            \end{aligned}
          \end{aligned}
          \label{eq:DOP_local}
        % $}
    \end{equation*}

  }
  \only<2->{\begin{equation*}
    \begin{matrix}
      \underset{\vec{U}_i(k)}{\mathrm{minimize}}& \overbrace{\frac{1}{2}{\vec{U}_i(k)}^T \alert<3>{H_i}\vec{U}_i(k)+{\alert<4>{\vec{f}_i(k)}}^T\vec{U}_i(k)}^{\textstyle J_{i}(\vec{\theta}_{i})}\\
      \mathrm{s.t.}&\Theta_{i}\vec{U}_i(k)=\vec{\theta}_{i}:\alert<5>{\vec{\lambda}_{i}}\\
    \end{matrix}
  \end{equation*}
  }
  \only<6->{
    \begin{equation*}
      \vec{\lambda}_{i}=-\alert<7>{P_{i}}\vec{\theta}_{i}-\alert<8>{\vec{s}_{i}(k)}
    \end{equation*}
    \centering
    where ${\alert<7>{P_{i}}={(\Theta_{i}H_{i}^{-1}\Theta_{i}\T)}^{-1}}$ and ${\alert<8>{\vec{s}_{i}(k)}=P_{i}\Theta_{i}H_{i}^{-1}\vec{f}_{i}(k)}$
  }
\end{frame}

\subsection{Detection Mechanism}
\begin{frame}{Detection}
\begin{assumption}
  We know nominal $\bar{P}_{i}$
\end{assumption}
\pause
\begin{assumption}
  Attacker chooses $\tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i})=T_{i}(k)\vec{\lambda}_{i} $
  $\to$ $-T_{i}(k)P_{i}\vec{\theta}_{i}-T_{i}(k)\vec{s}_{i}(k)$
\end{assumption}
\pause
\begin{itemize}
  \item We can estimate%
        \footnote[1]{Using Recursive Least Squares}
        $\hat{P}_{i}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)$ such as:
        \begin{equation*}
          \label{eq:lambdafuntheta_tilde}
          \tilde{\vec{\lambda}_{i}}=\gamma_{i}(\vec{\lambda}_{i}(\vec{\theta}_{i}))=-\widehat{\tilde{P}_{i}}(k)\vec{\theta}_{i}-\widehat{\tilde{\vec{s}}}_{i}(k)
        \end{equation*}
\pause
\item If $\widehat{\tilde{{P}}}_{i}(k)\neq\bar{{P}}_{i}$ $\to$ Attack
\end{itemize}
\end{frame}

\begin{frame}{About Estimation}
  \centering
  \begin{itemize}
    \item We estimate $\hat{P}_{i}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)$ simultaneously using Recursive Least Squares
          \pause
    \item Problem: Estimation during negotiation fails
          \pause
          \begin{itemize}
            \item Consecutive $\vec{\lambda}_{i}^{p}$ and $\vec{\theta}_{i}^{p}$ are linearly dependent $\to$ low input excitation
          \end{itemize}
          \pause
    \item Solution: Send sequence of random values of $\vec{\theta}_{i}$ until estimates converge
  \end{itemize}
\end{frame}

\begin{frame}{Detection}{In detail}
  \begin{itemize}
    \item Error ${E_{i}(k) =\|\widehat{\tilde{P}}_{i}(k)-\bar{P}_{i}\|_{F}}$
          \pause
    \item Create threshold $\epsilon_{P}$
          \pause
    \item Indicator ${d_{i}\in\{0,1\}}$ detects the attack in agent $i$.
          \pause
    \item $d_{i}=1$ if $E_{i}(k)>\epsilon_{P}$, $0$ otherwise
  \end{itemize}
\end{frame}

\subsection{Mitigation Mechanism}

\begin{frame}{Mitigation}
  \begin{itemize}
    \item Main idea: Reconstruct $\vec{\lambda}_{i}$ and use in negotiation
  \end{itemize}
  \pause
  \begin{assumption}
    We suppose ${\tilde{\vec{\lambda}}_{i}=\vec{0}}$ only if ${\vec{\lambda}_{i}=\vec{0}}$, which implies $T_{i}(k)$ invertible.
\end{assumption}\pause
\begin{itemize}
  \item Estimate the inverse of $T_{i}(k)$
        \begin{equation*}
          {\widehat{T_{i}(k)^{-1}}=\bar{P}_{i}\widehat{\tilde{P}_{i}}(k)^{-1}}
        \end{equation*}
        \pause
  \item Reconstruct $\vec{\lambda}_{i}$
        \begin{equation*}
          {\vec{\lambda}_{i}}_{\mathrm{rec}}=\widehat{T_{i}(k)^{-1}} \tilde{\vec{\lambda}_{i}} =-\bar{P}_{i}\vec{\theta}_{i}-\widehat{{T_{i}(k)^{-1}}}\widehat{\tilde{\vec{s}}}_{i}(k)
        \end{equation*}

\end{itemize}
\end{frame}

\subsection{Complete Mechanism}

\begin{frame}{Complete Mechanism}
  \begin{minipage}[c]{.45\linewidth}
    \begin{figure}[b]
      \centering
      \scalebox{.7}{\footnotesize \def\svgwidth{12cm}
      \input{../img/diagQuantSafe2.pdf_tex}}
      % \caption{Scheme for Secure DMPC}\label{fig:schemeSafeQuantity}
    \end{figure}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{.45\linewidth}
    Two phases:
    \begin{enumerate}
      \item Detect which agents are non-cooperative
      \item Reconstruct $\vec{\lambda}_{i}$ and use in negotiation
    \end{enumerate}
  \end{minipage}
\end{frame}

% \begin{frame}
% \SetKwBlock{negotPhase}{ Negotiation Phase:}{}
% \SetKwBlock{detectPhase}{ Detection Phase:}{}
% \scalebox{.8}{  \begin{algorithm}[H]
%     \DontPrintSemicolon
%     \detectPhase{
%     $h:=0$\;
%     \Repeat{
%     $\|\eta_{i}^{h}-\eta^{h-1}\|\leq\epsilon$
%   }{
%     Coordinator sets random $\vec{\theta}_{i}^{(h+1)}$ \;
%     Subsystems solve~\eqref{eq:DOP_local}, and send $\vec{\lambda}^{\star}_{i}(\vec{\theta}^{(h)})$\;
%     Coordinator estimates $\widehat{\tilde{P}}_{i}(k)^{(h)}$ and $\widehat{\tilde{\vec{s}}}_{i}(k)^{(h)}$ \;
%     $h:=h+1$\;
%   }
%     Coordinator computes $d_{i}$ using~\eqref{eq:2}\;
%   }
%     \negotPhase{
%     Coordinator initializes $\vec{\theta}^{(0)}$ \;
%     $p:=0$\;

@@

\begin{frame}{Secure DMPC}
  \begin{figure}[h]
    \centering
  \scalebox{.55}{
    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
      \draw[loosely dashed,
      minimum width=2.5cm,
      minimum height=1cm] (8cm,1cm) -- (8cm,-10cm);

@@

\section{Results}

\begin{frame}{Example}
  \begin{exampleblock}{Temperature Control of 4 Distinct Rooms Under Power Scarcity}
    \begin{itemize}
      \item 4 distinct rooms modeled using 3R-2C
      \item Initial temperature under $20^{o}\mathrm{C}$
      \item Not enough power to achieve setpoint $\left({\sum_{i=1}^{4} \vec{u}_{i}(k)\leq4\mathrm{kW}}\right)$
      \item Simulated for a period of ${5} \mathrm{h}$
      \item ZOH ${T_{s}=0.25\mathrm{h}}$
    \end{itemize}
  \end{exampleblock}
\end{frame}

\begin{frame}{Results}{Temporal}
  \begin{minipage}[c]{.5\linewidth}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\textwidth]{AirTempAndDecisionVariable.pdf}
      % \caption{Temperature in room I and the decision variable $E_{I}(k)$}\label{fig:response3Scenarios}
    \end{figure}
  \end{minipage}
  \hfill
  \begin{minipage}[c]{.45\linewidth}
    \begin{itemize}
      \item[N] Nominal
      \item[S] Selflish behavior
      \item[C] selfish behavior with Correction
    \end{itemize}
  \end{minipage}
\end{frame}

\begin{frame}
\frametitle{Results}
  \begin{table}[t]
  \centering
  \caption{Comparison of costs $J_{i}^{N}$ and $J_{G}^{N}$}\label{tab:costsGlobalLocal}
  \begin{tabular}[t]{cccc} \toprule
    Agent  & Nominal & Selfish & Selfish + correction\\
    \midrule
    I      & 103  &  64  & 104  \\
    II     &  73  &  91  &  73  \\
    III    & 100  & 123  & 101  \\
    IV     & 132  & 154  & 131  \\
    Global & 408  & 442  & 409  \\
    \bottomrule
  \end{tabular}
\end{table}

\end{frame}
\section*{Summary}

\begin{frame}{Summary}
  \pause
  \begin{minipage}[t]{.45\textwidth}
    % Keep the summary *very short*.
    \begin{enumerate}
      \item
            Resource allocation based DMPC is vulnerable to attacks.
            \pause
      \item
            Sub-problems' structure has time invariant parameters.
            \pause
      \item Attacks can be detected using these parameters.
            \pause
      \item Effects can be mitigated.
    \end{enumerate}
  \end{minipage}
  \pause
    % The following outlook is optional.
    % \vskip0pt plus.5fill
  \begin{minipage}[t]{.45\textwidth}
    \begin{itemize}
      \item Outlook
            \pause
            \begin{itemize}
              \item
                    Inequality Constraints yield Hybrid behavior
                    \pause
              \item
                    Non-linear attack model
            \end{itemize}
    \end{itemize}
  \end{minipage}
\end{frame}

@@

  \end{thebibliography}
\end{frame}
\begin{frame}[plain]
  \centering
  \vfill
  Questions?
  \vfill
  \begin{minipage}[t]{.45\linewidth}
    \small
    \centering
    Repository
    \href{https://github.com/Accacio/SysTol-21}{https://github.com/Accacio/SysTol-21}
